### 2015-12-17 source/24/Epigraphy and onomastics in Hesperia databank-template.tex
all biblio in EAGLE.bib

>>>>

CTS = Canonical Text Services (protocol to cite digitally-available texts in a canonical way).

EAGLE = The Europeana network of Ancient Greek and Latin Epigraphy: \ http://www.eagle-network.eu/

IEs = Integrating Digital Epigraphies project.

LGPN = The Lexicon of Greek Personal Names: http://www.lgpn.ox.ac.uk/

Pleiades = A community-built gazetteer and graph of ancient places: \ http://pleiades.stoa.org/

SNAP = Standards for Networking Ancient Prosopographies project: http://snapdrgn.net/

Trismegistos = Interdisciplinary portal of papyrological and epigraphical resources formerly Egypt and the Nile valley
(800 BC-AD 800): http://www.trismegistos.org/
